A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-11-06 CWP/papers/HSF-CWP-2017-01_roadmap/latex/cwp-main.tex
Avoid confusion of "promoting champions", use clearer phrase

\begin{itemize}
\item
  To provide training opportunities for developers; this should include
  the support to the software schools for young scientists and computer
  engineers, and of a permanent training infrastructure for accomplished
  developers;
\item
  To provide career support for developers, for instance by listing job
  opportunities and by helping to shape well-defined career paths that
  provide advancement opportunities on a par with those in, for example,
  detector construction;
\item
  To increase the visibility of the value of software developers in HEP,
  recognising that it has scientific research value on an equal footing
  with other activities, and acknowledging and promoting specific
  ``champions'' in the field.
\end{itemize}

>>>>

\begin{itemize}
\item
  To provide training opportunities for developers; this should include
  the support to the software schools for young scientists and computer
  engineers, and of a permanent training infrastructure for accomplished
  developers;
\item
  To provide career support for developers, for instance by listing job
  opportunities and by helping to shape well-defined career paths that
  provide advancement opportunities on a par with those in, for example,
  detector construction;
\item
  To increase the visibility of the value of software developers in HEP,
  recognising that it has scientific research value on an equal footing
  with other activities, and acknowledging and advocating for researchers
  who choose this as their speciality.
\end{itemize}
